\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4in, top=0.4in, right=0.4in, bottom=0.4in]{geometry} % Document margins
\usepackage{hyperref} % For hyperlinks

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Aniket Varma} % Your name
\address{+91 75066 38380 \\ Ghatkopar, Mumbai} 
\address{\href{mailto:vaan.origin@gmail.com}{vaan.origin@gmail.com} \\ \href{https://www.linkedin.com/in/varma-aniket/}{linkedin.com/in/varma-aniket} \\ \href{https://www.github.com/vaan-github}{github.com/vaan-github}}

\begin{document}

%----------------------------------------------------------------------------------------
% OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}
Aspiring IT professional with a Bachelor’s degree in Information Technology, skilled in JavaScript and the MERN stack. Driven by a passion for innovation and continuous learning, I am eager to apply my technical expertise to solve complex challenges and contribute to impactful projects. Open to exploring new technologies and committed to making a meaningful impact in a dynamic work environment.
% Your objective statement goes here.

\end{rSection}

%----------------------------------------------------------------------------------------
% EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering}, Mumbai University \hfill CGPA : 8  \hfill 2024  \\
Course: Information Technology

{\bf HSC}, RJ College of Science and Commerce \hfill Percentage : 70 \hfill 2020  
\\ Course: Computer Science (PCM)

{\bf SSC}, Our Lady of Good Health High School \hfill Percentage : 91.40 \hfill 2018

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHNICAL STRENGTHS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical skills & \href{https://github.com/vaan-github/JavaScript}{JavaScript}, React.js, Node.js, MERN Stack, \href{https://github.com/vaan-github/JavaTheCompleteReference}{Java} SQL, \href{https://github.com/vaan-github/DSA-JAVA-CODES}{Data Structure and Algorithm}.
\\ Soft Skills & Communication, Teamwork, Problem-solving, Adaptability, Leadership, Good Aptitude.  

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}

\textbf{Summer Intern - Fundamental and Application of Robotics Lab} \hfill Aug 2021 - Sep 2021\\
Shree L.R. Tiwari College of Engineering \href{https://drive.google.com/file/d/13E8hxdT5_Z6wY_oAUD6v-tK2hHk8x2a8/view?usp=sharing}{   [Completion Certificate]} \hfill \textit{Mira Road, Mumbai}
\begin{itemize}
    \item Completed a 60-hour certified internship with the Research and Development Department, in collaboration with MHRD and IIT Bombay, focusing on robotics fundamentals and applications. Gained hands-on experience through practical robotics projects, applying key concepts learned during the program.
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS}
\begin{itemize}
    \item Certified for presenting the major project "SmartSpeak: AI Voice Assistant" at the 2nd International Conference on Advanced Technologies and Management (ICATM-2024), with the research paper published in the ICATM-2024 journal.\href{https://drive.google.com/file/d/1WaL93tJuPJN1cGxox7ekrVcnih9mXzwu/view?usp=sharing}{[Certificate]}
    
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}

 \textbf{SmartSpeak: AI Voice Assistant} \\
Developed an AI-powered voice assistant using TypeScript, HTML, CSS, and JavaScript, featuring chatbot interaction, image processing, and voice commands. Recognised in a published paper and used as a final-year project, showcasing advanced AI and user engagement. \href{https://github.com/vaan-github/SMART-SPEAK-AI-VOICE-ASSISTANT}{[Major Project Repository]}

\item \textbf{JavaScript Projects} \\ 
Developed five JavaScript projects utilizing DOM manipulation, HTML, and CSS, as part of a personal learning initiative. \href{https://github.com/vaan-github/JavaScript/tree/main/7_Projects}{[Explore the Projects Here]}

\item \textbf{MERN Project} \\ 
Developed and deployed a MERN stack project, mastering authentication, REST APIs, front-end, back-end, MongoDB, Express.js, React, Node.js and encryption. Created a Login-Sign-Up Service App with a dedicated API and robust back-end. \href{https://github.com/vaan-github/mern_login_signup_react-native.git}{[Frontend Repository]} \href{https://github.com/vaan-github/Server_mern_login_signup_react-native.git}{[Backend Repository]}

\end{rSection}

%----------------------------------------------------------------------------------------
% EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Extra-Curricular Activities} 

\begin{itemize}
    \item Actively maintaining my \href{https://github.com/vaan-github}{GitHub Repository} and occasionally reading JavaScript articles on \href{https://medium.com/}{Medium}.
    \item Exploring tools like \href{https://github.com/termux}{Termux} and \href{https://github.com/RikkaApps/Shizuku}{Shizuku} that help optimize Android devices.
\end{itemize}

\end{rSection}

\end{document}